A minimal reaction-diffusion neural model generates {\emph{C. elegans}} undulation

### 2020-04-29 paper.tex
Fix Jenny's name
Co-authored-by: Jenny Magnes <jemagnes@vassar.edu>
temporary changes for pgfplots
this really needs to be better.
Review changes

\author[2]{Jennifer Magnes}

@@

\section{The model central pattern generator}

% TODO confirm the Xu reprint policy

@@

% TODO: remove Morris-Lecar
% remark that if the w and v nullclines come near each other, you see a critical slowdown.
% In Hodgkin-Huxley notation, $n$ is the potassium channel.  In the FHN formulation, this corresponds to the $w$ gate variable.
\begin{figure}[h!]
    \label{fig: nm nullclines}
    \centering
    \inputtikz{figures/neuron_dynamics/neuron_dynamics}
    % TODO: change legend to dv/dt=0, dw/dt=0
    % relabel ``real c. elegans'' to C. elegans (experimental data).
    % for publication: remove ticklabels, keep minor grid
    \caption{Nullclines of several different neuronal models; on the right is the biological model of Xu et al, in the centre is the Morris-Lecar model, and to the right is the FitzHugh-Nagumo model.  These have been arranged in order of decreasing complexity.}
\end{figure} % TODO: legend

@@

The simulation was performed in Python, using the standard SciPy ODE solvers, which wrap LSODA. % TODO list solver here

@@

We realize the network shown in \Fref{fig: cpg} into a system of ODEs, and solve it.  The equations are integrated, giving a timeseries of neuronal potentials.  These are passed through filters to simulate muscular movement and the resistance of the medium.  We used Gaussian smoothing and B-splines for this purpose.

@@

While the angle which a worm crawling on agar subtends tends to be oblique, as the constraint on the worm decreases, the angle becomes more and more acute - consider the videos . It is not hard to see that a fully unconstrained worm might behave much like our model does.

@@

% \begin{figure}
%
% \end{figure}

>>>>

\author[2]{Jenny Magnes}

@@

% TODO - acknowledge prior work by Izquierdo et al.  May be more biologically relevant.  The role of this paper is to show a very minimal example.  We slightly modified the original FHN.
\section{The model central pattern generator}

% TODO confirm the Xu reprint policy
% TODO show how the latest paper describes a small sequence of neurons forming coupled oscillators.

@@

% TODO: remove Morris-Lecar
% remark that if the w and v nullclines come near each other, you see a critical slowdown.
% In Hodgkin-Huxley notation, $n$ is the potassium channel.  In the FHN formulation, this corresponds to the $w$ gate variable.
\begin{figure}[h!]
    \label{fig: nm nullclines}
    \centering
    \inputtikz{figures/neuron_dynamics/neuron_dynamics}
    % TODO: change legend to dv/dt=0, dw/dt=0
    % relabel ``real c. elegans'' to C. elegans (experimental data).
    % for publication: remove ticklabels, keep minor grid
    % Replace the figure with Xu's
    % note that in the vicinity of the v-nullcline, the w-nullcline is essentially straight.
    \caption{Nullclines of several different neuronal models; on the right is the biological model of Xu et al, in the centre is the Morris-Lecar model, and to the right is the FitzHugh-Nagumo model.  These have been arranged in order of decreasing complexity.}
\end{figure} % TODO: legend

@@

We performed the simulations in Python, using the standard SciPy ODE solvers, which wrap LSODA. % TODO list solver here

@@

We realize the network shown in \Fref{fig: cpg} into a system of ODEs, and solve it.  The equations are integrated, giving a timeseries of neuronal potentials.  These were passed through filters to simulate muscular movement and the resistance of the medium.  We used Gaussian smoothing and B-splines for this purpose.

@@

While the angle which a worm crawling on agar subtends tends to be oblique, as the constraint on the worm decreases, the angle becomes more and more acute - consider the videos.  It is not hard to see that a fully unconstrained worm might behave much like our model does.

The worm generates sinusoidal oscillations

% Closely related to the first I&B (2008).  Alternate and likely more realistic structure with a distributed CPG was proposed by new Izquierdo.

@@

\begin{figure}[h!]
    \centering
    \pgfplotsset{}
    \inputtikz{figures/anal_sim_comp/anal_sim_comp}
    \caption{Comparison between simulated dynamics (top row) and observed dynamics in circuit (bottom row).}
    \label{fig: anal_sim_comp}
\end{figure}

% TODO: write up a section on the Beer paper and see how it relates to our CPG model.
